\vspace{-0.25em}\thetitle

### 2009-07-23 paper.tex
...

At this point it may be wise to address what we mean by prediction.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flow behavior is nondeterministic---flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
When compared with a specific outcome, such a prediction cannot be said to be ``wrong'' or ``right.''
How then can one measure the quality of a predicted distribution of outcomes?
This subtle and difficult issue is central to our evaluation methodology.

@@

The most fundamental tool for investigating linear structure in high dimensions is the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix and factors it into a product of three real matrices:
\begin{align}
  X = US\trans{V}.
\end{align}
Here $U$ and $V$ are orthogonal and $S$ is diagonal, with entries of decreasing nonnegative value.
Among the useful properties of this factorization, if all but the first $k$ diagonal entries of $S$ are zeroed out, the product $US_k\trans{V}$ is the best rank-$k$ approximation of $X$ under the Frobenius matrix norm.
The rows of $US_k$ can thus be viewed as an optimal $k$-dimensional reduced model of the rows of $X$, with a new coordinate system given by the columns of $V$.

@@

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traces.} 
\fig{svd}
\end{center}
\vspace{-0.85em}
\end{figure}

Clearly visible in \Figure{svd} is linear structure:
points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling along subspaces of three or more dimensions appear as ``smears.''

>>>>

At this point, it may be wise to address what we mean here by prediction.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flow behavior is nondeterministic---flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
When compared with a specific outcome, such a prediction cannot be said to be ``wrong'' or ``right.''
How then can one measure the quality of a predicted distribution of outcomes?
This subtle and difficult issue is central to our evaluation methodology.

@@

The foremost tool for investigating linear structure in high dimensions is the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix and factors it into a product of three real matrices:
\begin{align}
  X = US\trans{V}.
\end{align}
Here $U$ and $V$ are orthogonal and $S$ is diagonal, with entries of decreasing nonnegative value.
Among the useful properties of this factorization, is that the product $US_k\trans{V}$ is the best rank-$k$ approximation of $X$ under the Frobenius matrix norm, where $S_k$ is the matrix $S$ with all but the first $k$ diagonal entries zeroed out.
The $k$ initial coordinates of the rows of $US_k$ can thus be viewed as an optimal $k$-dimensional reduced model of the rows of $X$, with a new coordinate system given by the columns of $V$.

@@

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traces.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure}

Linear structure is clearly visible in \Figure{svd}:
the points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling along subspaces of three or more dimensions appear as ``smears.''
